Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-02-23 fertile.Rmd
more citations + lit review of packages

bibliography: [bibliography.bib, pkgs.bib]
output: rticles::asa_article
---

@@

There also exists a small selection of R packages that work to address the issue of research reproducibility, though not all of them are available on `CRAN`. **rrtools** [@R-rrtools], developed to address some of the issues discussed in @marwick2018packaging, creates a basic R package structure for a data analysis project and implements a basic **testthat** `check` functionality.

orderly
• Based on the step-by-step analysis process. 
• Build components that take inputs from other components
• Have to declare project structure at the beginning.

workflowr
• Focused a lot on version control and making code available

checkers
• Allows you to create custom checks to look over your work

*Notes: Almost all of these are things you need to do before you start your project. They each focus on a small subset of reproducibility components. They are somewhat complicated to use -- commands are complex and there are often a lot of them.

@@

```{r}
dir
fs::dir_ls(dir) %>% head()
```

```{r}
new_dir
fs::dir_ls(new_dir) %>% head()
```

>>>>

bibliography: [bibliography.bib, pkgs.bib]
output: rticles::asa_article

---

@@

There also exists a small selection of R packages that work to address the issue of research reproducibility, though not all of them are available on `CRAN`.

**rrtools** [@R-rrtools], developed to address some of the issues discussed in @marwick2018packaging, creates a basic R package structure for a data analysis project and implements a basic **testthat**::`check` functionality. The **orderly** [@R-orderly] package also focuses on file structure, requiring the user to declare a desired project structure (typically a step-by-step structure, where outputs from one step are inputs into the next) at the beginning and then creating the files necessary to achieve that structure. **workflowr**'s [@R-workflowr] functionality is based around version control and making code easily available online. It works to generate a website containing time-stamped, versioned, and documented results. **checkers** [@R-checkers] allows you to create custom checks that look at different aspects of reproducibility. **packrat** [@R-packrat] is focused on dependencies, creating a packaged folder containing a project as well as all of its dependencies, so that projects dependent on lesser-used packages can be easily shared across computers. Lastly, the **reproducible** [@R-reproducible] package focuses on the concept of caching--saving information so that projects can be run faster each time they are re-completed from the start.

Many of these packages focus on one specific area of reproducibility, and while they each succeed well at their intended goal, they are not necessarily the most practical option for users trying to address a wide variety of factors influencing reproducibility at once.

Additionally, with the focused nature of these packages comes added complexity. The functions in these packages are often quite complex to use, and many steps must be completed to achieve the required reproducibility goal. This complex nature means that most reproducibility packages currently available are not easily accessible to users near the beginning of their R journey, nor particularly useful to those looking for quick and easy reproducibility checks.

@@

\tiny
```{r}
dir
fs::dir_ls(dir) %>% head()
```

```{r}
new_dir
fs::dir_ls(new_dir) %>% head()
```
\normalsize
